---
editor_options: 
  chunk_output_type: console
---
# Repeatability of distance moved

```{r}
library(data.table)
library(dplyr)

library(lme4)
library(rptR)
```

## Prepare data

### Read data

```{r}
paths = list.files(path = "data/lt_tracks", full.names = T)

# read files
data = lapply(paths, fread)

# bind data
data = rbindlist(data)[type != "interf"]

# remove all weights
data_move = data[, !(c(sprintf("wt_%i", seq(8)), "gen"))]

# assign strategy
data_move[, comp_strat := fifelse(data$wt_5 > 0, "forager", "klept")]
data_move[type == "exploit", comp_strat := "forager"]
```

### Summarise over intervals

```{r}
data_move = data_move[, list(
  mean_distance = mean(distance),
  sd_distance = sd(distance),
  mean_r = mean(mean_r)
), by = c("id", "interval", "growth", "type", "rep_", "comp_strat")]

# save
fwrite(
  data_move,
  file = "data/data_for_rpt.csv"
)
rm(data)
```

## Scale data

```{r}
data_move[, c("mean_distance", "sd_distance", "mean_r") := 
            lapply(.SD, scales::rescale), 
          by = c("growth", "type", "rep_", "interval"),
          .SDcols = c("mean_distance", "sd_distance", "mean_r")]
```

## Repeatability analysis

### Functions for repeatability

```{r}
# basic function for repeatability
get_repeatability = function(df) {
  rptR::rpt(mean_distance ~ mean_r + (1 | id) + (1 | interval), 
            grname = "id", 
            data = df, 
            datatype = "Gaussian", nboot = 100, npermut = 10)
}

# function for repeatability that accounts for
# competitive strategy as a fixed effect
get_repeatability_strat = function(df) {
  rptR::rpt(mean_distance ~ mean_r + comp_strat + (1 | id) + (1 | interval), 
            grname = "id", 
            data = df, 
            datatype = "Gaussian", nboot = 100, npermut = 10)
}
```

### Get repeatabilities in scenario 1

```{r}
# nest data from scenario 1
data_sc1 = data_move[type == "exploit", list(
  data = list(.SD)
), by = c("growth", "type", "rep_")]

# apply function over nested data
data_sc1[, mod_rpt := lapply(data, get_repeatability)]

data_sc1[, c("rpt_v", "rpt_se") := list(
  vapply(mod_rpt, function(m) m$R$id[1], FUN.VALUE = 1.0),
  vapply(mod_rpt, function(m) m$se$se[1], FUN.VALUE = 1.0)
)]
```

### Repeatability not accounting for competition strategy

```{r}
# nest data from scenario 2
data_sc2 = data_move[type == "obligate" & growth <= 0.02, list(
  data = list(.SD)
), by = c("growth", "type", "rep_")]

# apply function over nested data
data_sc2[, mod_rpt := lapply(data, get_repeatability)]

data_sc2[, c("rpt_v", "rpt_se") := list(
  vapply(mod_rpt, function(m) m$R$id[1], FUN.VALUE = 1.0),
  vapply(mod_rpt, function(m) m$se$se[1], FUN.VALUE = 1.0)
)]
```

### Repeatability accounting for competition strategy

```{r}
# nest data from scenario 2
data_sc2_strat = data_move[type == "obligate" & growth <= 0.02, list(
  data = list(.SD)
), by = c("growth", "type", "rep_")]

# apply function over nested data
data_sc2_strat[, mod_rpt := lapply(data, get_repeatability_strat)]

data_sc2_strat[, c("rpt_v", "rpt_se") := list(
  vapply(mod_rpt, function(m) m$R$id[1], FUN.VALUE = 1.0),
  vapply(mod_rpt, function(m) m$se$se[1], FUN.VALUE = 1.0)
)]
```

### Repeatability splitting by competition strategy

```{r}
# select data from scenario 2
data_sc2_split = data_move[type == "obligate" & growth <= 0.02]

# split by strategy
data_sc2_split = data_sc2_split[, list(
  data = list(.SD)
), by = c("growth", "type", "rep_", "comp_strat")]

# apply function over nested data
data_sc2_split[, mod_rpt := lapply(data, get_repeatability)]

data_sc2_split[, c("rpt_v", "rpt_se") := list(
  vapply(mod_rpt, function(m) m$R$id[1], FUN.VALUE = 1.0),
  vapply(mod_rpt, function(m) m$se$se[1], FUN.VALUE = 1.0)
)]
```

## Prepare data for plotting

```{r}
# add identifier
Map(
  list(data_sc1, data_sc2, data_sc2_strat, data_sc2_split),
  list("sc1", "sc2", "sc2_strat", "sc2_split"),
  f = function(df, nm) df[, treat := nm]
)
```

```{r}
data_rpt = Map(
  list(data_sc1, data_sc2, data_sc2_strat, data_sc2_split),
  f = function(df) df[, !c("data", "mod_rpt")]
)
```

```{r}
# save as Rds object
save(
  data_rpt,
  file = "data/data_rpt.Rds"
)
```
